### 2021-03-01 paper.Rmd
LaTeX fix (extra open `{`)

Data: $X_{{n \times p}$, 
Basis: $A_{p \times d}$, commonly 1d or 2d projection, orthonormality, more displays in the next section - can display a matrix A, Link to geometry properties.
projection: $Y = X \cdot A$

>>>>

Data: $X_{n \times p}$, 
Basis: $A_{p \times d}$, commonly 1d or 2d projection, orthonormality, more displays in the next section - can display a matrix A, Link to geometry properties.
projection: $Y = X \cdot A$
